Parsing Postfix log files

### 2007-12-07 doc/logparser.tex
Made hyperref work again.
I want to be able to use pdftex as well as latex, which requires major restructuring of the Makefile; as a side effect the build process will be greatly improved.  Having thoroughly broken the build process, it's now back in a reasonable and working state, so I'm committing even though the changes aren't finished.

% Useful stuff for math mode.
\usepackage{amstext}
% Wrapping of URLs.
\usepackage{url}
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
% Change how nested enumerate environments are labelled.
\renewcommand{\labelenumii}{\roman{enumii}:}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}

@@

% XXX THIS DOESN'T WORK AFTER PACKAGE UPGRADES :(
% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author don't work - I think either gnuplot or graphviz clobbers it.
%\usepackage{hyperref}
%\hypersetup{
%    pdftitle    = {Parsing Postfix log files},
%    pdfauthor   = {John Tobin},
%    final       = true,
%    pdfborder   = {0 0 0},
%%    breaklinks  = true,
%}
%\usepackage{breakurl}
\usepackage{lastpage}

@@

\showgraph{build/logparser-flow-chart-part-1.ps}{Parser flow chart part
1}{flow chart image part 1}

\showgraph{build/logparser-flow-chart-part-2.ps}{Parser flow chart part
2}{flow chart image part 2}

@@

\showgraph{build/plot-normal-filesize-numlines.ps}{Execution time vs file
size vs number of lines}{execution time vs file size vs number of lines
graph}

@@

\showgraph{build/plot-normal-filesize-numlines-factor.ps}{Ratio of file
size and number of lines to execution time}{execution time vs file size vs
number lines factor}

@@

\showgraph{build/plot-normal-shuffle-factor.ps}{Percentage increase of
shuffled over normal}{percentage increase of shuffled over normal}

\showgraph{build/plot-normal-reverse-factor.ps}{Percentage increase of
reversed over normal}{percentage increase of reversed over normal}

@@

\showgraph{build/plot-cached-discarded.ps}{Regex: cached vs
discarded}{normal regex vs discard regex}

\showgraph{build/plot-cached-discarded-factor.ps}{Regex caching: percentage
execution time increase}{normal regex vs discarded regex factor}

@@

\showgraph{build/plot-hits.ps}{Hits per rule}{rule hits graph}

@@

\showgraph{build/plot-hits-low.ps}{Hits per rule (low)}{hits per rule low}

@@

\showgraph{build/plot-hits-middle.ps}{Hits per rule (middle)}{hits per rule
middle}

\showgraph{build/plot-hits-high.ps}{Hits per rule (high)}{hits per rule
high}

>>>>

% Useful stuff for math mode.
\usepackage{amstext}
% Wrapping of URLs; this doesn't work in the bibliography, but the breakurl
% package does.
%\usepackage{url}
% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\PLP{}}
\newcommand{\parsernames}{\PLP{}'s}
% Include images
\usepackage[final]{graphicx}
% Change how nested enumerate environments are labelled.
\renewcommand{\labelenumii}{\roman{enumii}:}
\renewcommand{\refname}{Bibliography}
% Add the bibliography into the table of contents.
\usepackage[section,numbib]{tocbibind}

@@

% When creating a \PDF{} make the table of contents into links to the pages
% (without horrible red borders) and include bookmarks.  The title and
% author don't work - I think either gnuplot or graphviz clobbers it.
% With later TeX versions the dvips argument is necessary; everywhere else
% suggests using pdftex as the argument, but pdftex doesn't know how to
% include postscript images, so I need to create a dvi, convert it to
% postscript, and convert that to PDF.  I might lookup how to include
% postscript with pdftex.
\usepackage[dvips]{hyperref}
\hypersetup{
    pdftitle    = {Parsing Postfix log files},
    pdfauthor   = {John Tobin},
    final       = true,
    pdfborder   = {0 0 0},
%    breaklinks  = true,
}
% This is necessary for URLs in the bibliography; I dunno why the url
% package doesn't work.
\usepackage{breakurl}
\usepackage{lastpage}

@@

\showgraph{build/logparser-flow-chart-part-1}{Parser flow chart part
1}{flow chart image part 1}

\showgraph{build/logparser-flow-chart-part-2}{Parser flow chart part
2}{flow chart image part 2}

@@

\showgraph{build/plot-normal-filesize-numlines}{Execution time vs file
size vs number of lines}{execution time vs file size vs number of lines
graph}

@@

\showgraph{build/plot-normal-filesize-numlines-factor}{Ratio of file
size and number of lines to execution time}{execution time vs file size vs
number lines factor}

@@

\showgraph{build/plot-normal-shuffle-factor}{Percentage increase of
shuffled over normal}{percentage increase of shuffled over normal}

\showgraph{build/plot-normal-reverse-factor}{Percentage increase of
reversed over normal}{percentage increase of reversed over normal}

@@

\showgraph{build/plot-cached-discarded}{Regex: cached vs
discarded}{normal regex vs discard regex}

\showgraph{build/plot-cached-discarded-factor}{Regex caching: percentage
execution time increase}{normal regex vs discarded regex factor}

@@

\showgraph{build/plot-hits}{Hits per rule}{rule hits graph}

@@

\showgraph{build/plot-hits-low}{Hits per rule (low)}{hits per rule low}

@@

\showgraph{build/plot-hits-middle}{Hits per rule (middle)}{hits per rule
middle}

\showgraph{build/plot-hits-high}{Hits per rule (high)}{hits per rule
high}
